resistanceModelNotesAndy

### 2016-02-11 resistanceModelNotesAndy.Rmd
notes

@@

~ run PRCC for difference between mix2 & sequential
~ might need to structure data differently

@@

1. I could add the combined mixture/individual (strategy 2) as a dotted line to plotcurtis_f2_generic()
(and then could even add labels of 1,2,3 to where they cross the 50% line)

>>>>

** 9/2/16 **
sent new figs of PRCC of diff between seq & mix2 to Ian

** 10/2/16 **

~ reran trees they show that effectiveness > ~ 0.7 & exposure < 0.7 favours mixture2 over sequential
~ this is consistent with my graphs of difference vs effect & exposure (therefore are the trees really necessary ?)

mix2 can already be displayed in plotcurtis_f2_generic() using addCombinedStrategy
I had just set default to F because the plot gets even more confusing.

Maybe add option to just plot mix2 ?

Also offer option to plot from : runcurtis_f2()

This which simply reduces effectiveness of insecticide2 from 1 to 0.85, makes seq better than mix (where mix was better for curtis).

runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )

@@

~ add default curtis values to UI labels in server.r
~ check on plotting of combined strategy
~

~ play with shiny app to help my understanding of how modifying the params alters results

~ check code in findResistancePointsMixResponsive()

@@
